\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.2cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{lmodern}
\usepackage{tikz}
\usepackage{mdframed}
\usepackage{ragged2e}
\usepackage[none]{hyphenat}

% Better margin and spacing control
\tolerance=1
\emergencystretch=30em
\usepackage{microtype}
\setlength{\parindent}{0pt}
\setlength{\RaggedRightParindent}{0pt}
\setlength{\parskip}{0.4em}

% Define colors
\definecolor{primary}{RGB}{0, 79, 159}
\definecolor{secondary}{RGB}{100, 100, 100}
\definecolor{accent}{RGB}{70, 142, 220}

% Modern font setup
\renewcommand{\familydefault}{\sfdefault}

% Section styling
\usepackage{titlesec}
\titleformat{\section}{\Large\bfseries\color{primary}}{\thesection}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries\color{secondary}}{\thesubsection}{0em}{}
\titlespacing*{\section}{0pt}{*0.8}{*0.4}
\titlespacing*{\subsection}{0pt}{*0.8}{*0.4}

% List settings
\setlist{nosep}
\setlist[itemize]{leftmargin=*}
\setlist[itemize]{label=\color{primary}{\small\textbullet}}

% Hyperlink styling
\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    filecolor=accent,
    urlcolor=accent,
}

\begin{document}

% Header with subtle decoration
\begin{tikzpicture}[remember picture,overlay]
\fill[primary] (current page.north west) rectangle ++(\paperwidth,0.4pt);
\end{tikzpicture}

\begin{center}
    {\color{primary}\Large\textbf{ABIN ZORTO}}\\[0.2em]
    {\color{secondary}\large\textbf{MACHINE LEARNING ENGINEER}}\\[0.3em]
    
    \small\color{secondary}
    \faMapMarker\ Flat 6, 60 West-ferry Road, London, E148LN |
    \faMobile\ +447939412710 |
    \faEnvelope\ abinzorto@outlook.com |
    \faLinkedin\ linkedin.com/in/abin-zorto
\end{center}

% Modified summary section
{\color{secondary}
Machine Learning Engineer specializing in customer analytics and marketing optimization, with expertise in lifetime value modeling and causal inference. Proven track record of developing and deploying end-to-end ML solutions that drove 30\%+ improvements in prediction accuracy and customer insights. Experience in marketing mix modeling and building scalable data pipelines that process millions of customer interactions. Strong focus on cross-functional collaboration and autonomous project delivery.
}

\section*{TECHNICAL SKILLS}
\textbf{Programming Languages:} Python, JavaScript, C++, C\#, R, SQL, NoSQL, Scala

\textbf{Machine Learning \& Data Science:} NumPy, Pandas, TensorFlow, PyTorch, Scikit-learn, Matplotlib, Seaborn, PySpark, NLTK, LangChain, LlamaIndex, Hugging Face Transformers

\textbf{Cloud \& Infrastructure:}
\begin{itemize}
    \item Azure: Machine Learning, Databricks, Functions, Kubernetes Service, DevOps, Active Directory, DataLake
    \item AWS: EC2, S3, Lambda, SageMaker, Glue, ECS, RDS, CloudWatch, CloudFormation
\end{itemize}

\textbf{Development \& DevOps:} Terraform, Docker, Kubernetes, Git, GitHub Actions, Jenkins, GitLab, MLflow, Weights \& Biases, Model Registry, Feature Store

\textbf{GenAI \& MLOps:} LangChain, LlamaIndex, Hugging Face Transformers, MLflow, Weights \& Biases, Model Registry, Feature Store

\section*{EXPERIENCE}

\subsection*{Senior Research Assistant}
\textbf{University of East London} \hfill September 2023 -- July 2024
\begin{itemize}
    \item Developed customer lifetime value (LTV) models processing 1M+ customer interactions, achieving 88\% prediction accuracy and enabling targeted marketing strategies
    \item Implemented marketing mix models to optimize resource allocation across channels, resulting in 25\% improved ROI
    \item Built causal inference models to measure campaign effectiveness, identifying 30\% uplift in customer engagement
    \item Engineered REST APIs handling 50,000+ daily requests for model serving using FastAPI and Docker
    \item Created automated A/B testing framework for marketing campaigns, improving conversion rates by 22\%
    \item Secured £50,000 research grant and led an 8-person team investigating vector-borne disease proliferation using GenAI models.
    \item Engineered an ML pipeline processing 100,000+ data points, achieving 92\% prediction accuracy.
    \item Architected a data visualization framework reducing analysis time by 40\% and boosting stakeholder engagement by 25\%.
    \item Orchestrated deployment of 3 production ML models using TensorFlow and PyTorch, increasing reliability by 35\%.
    \item Pioneered a bias detection system analyzing 5 key metrics, improving model fairness scores by 28\%.
    \item Scaled serverless computing infrastructure handling 50,000+ daily requests using Azure Functions.
    \item Established an automated CI/CD pipeline reducing model deployment time by 50%.
    \item Implemented GenAI solutions using LangChain and Hugging Face, reducing data processing time by 40\%.
    \item Established MLOps practices reducing model deployment cycle from 2 weeks to 2 days.
    \item Built customer segmentation models achieving 85\% accuracy in predicting customer behavior.
    \item Collaborated with cross-functional teams to integrate ML solutions into existing business processes, enhancing customer insights and driving strategic decisions.
\end{itemize}

\subsection*{Teaching and Research Supervisor}
\textbf{University of East London} \hfill May 2023 -- September 2023
\begin{itemize}
    \item Mentored 15 graduate students, achieving a 93\% project completion rate.
    \item Spearheaded 12 technical workshops reaching 100+ students, boosting engagement rates by 40\%.
    \item Redesigned course materials for 3 modules, elevating student satisfaction scores by 20\%.
    \item Guided 30 students to achieve a 35\% improvement in research paper quality.
    \item Mentored 5 students to successful publication, achieving a 40\% increase in department publication rate.
\end{itemize}

\subsection*{Junior Research Assistant}
\textbf{University of East London} \hfill September 2022 -- May 2023
\begin{itemize}
    \item Architected healthcare ML models achieving a 30\% improvement in diagnosis accuracy.
    \item Published 2 papers in Q2 journals (Impact Factor: 5), cited by 50+ researchers.
    \item Delivered 5 conference presentations reaching 1,000+ academic audience members.
    \item Optimized data processing pipeline to handle 5TB+ of medical data using PySpark.
    \item Designed analytics workflow reducing query time by 60\% using Azure Synapse.
    \item Collaborated with medical professionals to develop AI-driven diagnostic tools, enhancing patient outcomes.
\end{itemize}

\subsection*{Retention Specialist}
\textbf{Direct Line Group} \hfill January 2022 -- March 2022
\begin{itemize}
    \item Managed 200+ monthly customer interactions achieving a 95\% satisfaction rate.
    \item Formulated stakeholder feedback system capturing 50\% more actionable insights.
    \item Contributed to a 15\% reduction in customer churn through data-driven engagement strategies.
    \item Generated weekly analytics reports tracking 20+ KPIs for the executive team.
    \item Achieved top 10\% performance rating among 50+ specialists.
\end{itemize}

\section*{RESEARCH PUBLICATIONS}
\href{https://scholar.google.com/citations?hl=en&user=1yjR8x8AAAAJ}{scholar.google.com/citations?hl=en\&user=1yjR8x8AAAAJ} {\small\color{secondary}(click to view)}
\begin{itemize}
    \item Authored ML-based keratoconus diagnosis paper achieving an 85\% accuracy rate - \textbf{Informatics in Medicine Unlocked} (Impact Factor: 5.2) (Citations: 5+)
    \item Pioneered novel GAN architecture improving sepsis diagnosis accuracy by 25\% - \textbf{Applied Computational Intelligence}
\end{itemize}

\section*{TECHNICAL PROJECTS} 
\href{https://github.com/AbinZorto}{github.com/AbinZorto} {\small\color{secondary}(click to view)}

\textbf{Computer Vision \& Deep Learning}
\begin{itemize}
    \item Engineered YOLOv4 detection system achieving 64\% accuracy on 50,000+ video frames for COVID-19 compliance.
\end{itemize}

\textbf{MLOps \& Infrastructure}
\begin{itemize}
    \item Orchestrated an ML deployment system reducing the release cycle from 24 hours to 6 hours across 3 environments.
    \item Scaled compute infrastructure supporting 200+ concurrent users with 99.9\% uptime.
    \item Optimized CI/CD pipeline reducing build times by 40\% for 20+ microservices.
    \item Automated resource provisioning cutting deployment costs by 35\%.
    \item Integrated GenAI tools into CI/CD workflows, enhancing deployment intelligence and automation.
\end{itemize}

\textbf{NLP \& Document Processing}
\begin{itemize}
    \item Spearheaded a document analysis system processing 10,000+ pages daily with 92\% accuracy.
    \item Integrated 5+ Azure Cognitive Services achieving a 40\% improvement in text extraction.
    \item Scaled Kubernetes deployment to handle 100+ concurrent processing requests.
    \item Developed GenAI-based chatbots for automated document classification, improving processing speed by 50\%.
\end{itemize}

\textbf{Customer Analytics Platform}
\begin{itemize}
    \item Developed an end-to-end customer behavior prediction system processing 1M+ daily interactions.
    \item Implemented an A/B testing framework improving marketing campaign effectiveness by 25\%.
    \item Deployed GenAI-powered customer service automation reducing response time by 60\%.
    \item Leveraged MLOps practices to maintain and update predictive models, ensuring continuous improvement.
\end{itemize}

\section*{EDUCATION}

\textbf{PhD in Computer Science} \hfill May 2023 -- May 2026\\
University of East London\\
\textit{Research Focus:} A Multimodal Computational Intelligence Approach to Neurophysiological Predictors of Transcranial Direct Current Stimulation for Depression Treatment

\textbf{MSc Computer Science} \hfill January 2021 -- January 2023\\
University of East London \hfill Grade: Distinction (96\%)\\
\textit{Thesis:} Developed an ML system improving medical diagnosis accuracy by 30\%

\textbf{MSc Advanced Robotics} \hfill September 2019 -- September 2020\\
Queen Mary University of London \hfill Grade: Distinction (81\%)\\
\textit{Thesis:} Created an autonomous system reducing navigation errors by 55\%

\textbf{BEng Mechanical Engineering} \hfill September 2016 -- June 2019\\
The University of Manchester \hfill Grade: 2:2 (55\%)\\
\textit{Final Project:} Led a 4-person team to design an automated system improving efficiency by 30\%

\end{document}